Minimum Regret Search for Single- and Multi-Task Optimization

### 2016-06-15 2016_ICML/presentation/main.tex
Two minor bug fixes in presentation

\begin{itemize}
  \item Motivation: optimization of expensive target functions
  \item Examples:
  \begin{itemize}
    \item Automated machine learning (computational cost)
    \item Process optimization (economical cost)
    \item Robot learning (supervision cost)
    \item Animal testing (moral cost)
  \end{itemize}
  \pause
  \item Objective: Find close-to-optimal value of target function with a very small number of function evaluations (``queries'')
  \pause
   \item Approach: Invest significant amounts of computation to determine ``optimal'' sequence of query points
\end{itemize}
\vspace*{4cm}
\end{frame}

@@

  \begin{itemize}
    \item Contribution: Novel acquisition which explicitly aims at minimizing the expected simple regret
    \pause
    \item Additional content of the paper:
    \begin{itemize}
      \item multi-task minimum regret search
      \item results on simulated robotic task
    \end{itemize}
    \pause
    \item Future work:
    \begin{itemize}
      \item treatment of GP hyperparameters
      \item more efficient approximation techniques for MRS
    \end{itemize}
    \pause
    \item Source code available at: \url{https://github.com/jmetzen/bayesian_optimization}
  \end{itemize}

>>>>

\begin{itemize}
  \item Motivation: optimization of expensive target functions
  \item Examples:
  \begin{itemize}
    \item Automated machine learning (computational cost)
    \item Process optimization (economical cost)
    \item Robot learning (supervision cost)
    \item Animal testing (moral cost)
  \end{itemize}
  \pause
  \item Objective: Find close-to-optimal value of target function with a very small number of function evaluations (``queries'')
  \pause
   \item Approach: Invest significant amounts of computation time to determine ``optimal'' sequence of query points
\end{itemize}
\vspace*{4cm}
\end{frame}

@@

  \begin{itemize}
    \item Contribution: Novel acquisition function which explicitly aims at minimizing the expected simple regret
    \pause
    \item Additional content of the paper:
    \begin{itemize}
      \item multi-task minimum regret search
      \item results on simulated robotic task
    \end{itemize}
    \pause
    \item Future work:
    \begin{itemize}
      \item treatment of GP hyperparameters
      \item more efficient approximation techniques for MRS
    \end{itemize}
    \pause
    \item Source code available at: \url{https://github.com/jmetzen/bayesian_optimization}
  \end{itemize}
